Dominance Regions for Affine Cluster Algebras

### 2022-06-30 affine_dominance.tex
Modification

\newcommand{\Aut}{\operatorname{Aut}}
\newcommand{\Col}{\operatorname{Col}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\dpt}{\operatorname{dp}}
\newcommand{\hgt}{\operatorname{ht}}
\newcommand{\Id}{\operatorname{Id}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\obeta}{{\overline{\beta}}}
\newcommand{\oi}{{\overline{\imath}}}
\newcommand{\ot}{{\overline{t}}}
\newcommand{\rsh}{{\operatorname{rsh}}}
\newcommand{\sh}{{\operatorname{sh}}}
\newcommand{\WA}{{W\!\!A}}
\newcommand{\wt}{{\operatorname{wt}}}

@@

  Define an infinite quiver $\widehat{Q}$ with vertices $(k,s)\in [n]\times\ZZ_{\ge0}$ and the following arrows:
  \begin{itemize}
    \item an arrow $(\ell,s)\to (k,s)$ of weight $b_{k\ell}$ whenever $k<\ell$ and $s\ge0$;
    \item an arrow $(k,s+1)\to (\ell,s)$ of weight $-b_{k\ell}$ whenever $k<\ell$ and $s\ge0$;
    \item an arrow $(k,s+1)\to (k,s)$ of weight $-1$ whenever $s\ge0$.
  \end{itemize}
  Given a path $p$ in $\widehat{Q}$, write $\wt(p)$ for the product of the weights along the arrows in $p$.
  Let $i(p)$ and $t(p)$ denote the initial and terminal vertex along the path $p$.
  Write $\hgt(p)$ for the largest $s$ appearing as the second component of a vertex along the path $p$.
  Then for $r<0$ with $r=ns+\ell$ for $1\le\ell\le n$, we have
  \[\lambda'_k=\begin{cases}\sum\limits_{\substack{p\subset\widehat{Q}\\ \hgt(p)=-s-1, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $1\le k\le\ell-1$;}\\ \sum\limits_{\substack{p\subset\widehat{Q}\\ \hgt(p)=-s, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $\ell\le k\le n$;} \end{cases}\]

>>>>

\newcommand{\Aut}{\operatorname{Aut}}
\newcommand{\Col}{\operatorname{Col}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\dpt}{\operatorname{dp}}
\newcommand{\hgt}{\operatorname{ht}}
\newcommand{\Id}{\operatorname{Id}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\obeta}{{\overline{\beta}}}
\newcommand{\oi}{{\overline{\imath}}}
\newcommand{\ot}{{\overline{t}}}
\newcommand{\rsh}{{\operatorname{rsh}}}
\newcommand{\sh}{{\operatorname{sh}}}
\newcommand{\uleps}{{\underline{\varepsilon}}}
\newcommand{\WA}{{W\!\!A}}
\newcommand{\wt}{{\operatorname{wt}}}

@@

  Given a sequence of signs $\uleps=(\varepsilon_1,\varepsilon_2,\ldots)$ with $\varepsilon_i\in\{\pm\}$, define an infinite quiver $\widehat{Q}_\uleps$ with vertices $(k,s)\in [n]\times\ZZ_{\ge0}$ and the following arrows:
  \begin{itemize}
    \item an arrow $(\ell,s)\to (k,s)$ of weight $b_{k\ell}$ whenever $k<\ell$, $s\ge0$, and $\varepsilon_{ns+\ell}=-$;
    \item an arrow $(\ell,s+1)\to (k,s)$ of weight $-b_{k\ell}$ whenever $\ell<k$, $s\ge0$, and $\varepsilon_{ns+\ell}=-$;
    \item an arrow $(\ell,s+1)\to (\ell,s)$ of weight $-1$ whenever $s\ge0$.
  \end{itemize}
  Given a path $p$ in $\widehat{Q}$, write $\wt(p)$ for the product of the weights along the arrows in $p$.
  Let $i(p)$ and $t(p)$ denote the initial and terminal vertex along the path $p$.
  Write $\hgt(p)$ for the largest $s$ appearing as the second component of a vertex along the path $p$.
  Then for $r<0$ with $r=ns+\ell$ for $1\le\ell\le n$, we have
  \[\lambda'_k=\begin{cases}\sum\limits_{\substack{p\subset\widehat{Q}\\ \hgt(p)=-s-1, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $1\le k\le\ell-1$;}\\ \sum\limits_{\substack{p\subset\widehat{Q}\\ \hgt(p)=-s, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $\ell\le k\le n$;} \end{cases}\]
